Abstractions for Type-Level Programming

### 2022-04-19 article.tex
Do TODOs

\SystemFm's type rules enable any match expression to be typed as a match type, but the situation is different in the full Scala language.
Pattern matching in Scala supports many sorts of patterns~\citep{emir2007matching}, most of which do not have a match type counterpart.
Furthermore, typing match expressions as match types is not enabled by default in order to preserve backward compatibility.
Instead, explicit type annotations must be provided.
% TODO: Add examples

>>>>

\SystemFm's type rules enable any match expression to be typed as a match type, but the situation is different in the full Scala language.
Pattern matching in Scala supports many sorts of patterns~\citep{emir2007matching}, most of which do not have a match type counterpart.
Furthermore, typing match expressions as match types is not enabled by default in order to preserve backward compatibility.
Instead, explicit type annotations must be provided.

For example, consider the following function definition:

\begin{lstlisting}
def foo[X](x: X) = x match
  case x: Int => x.toString
  case x: String => x.toInt
\end{lstlisting}

In the absence of result type annotation, Scala's type inference will first assign \lstinline!String | Int! for the match expression, and then immediately widen that union to the least upper bound of left- and right-hand-side, |Any|, which will then be used as |foo|'s (inferred) result type.
To obtain a precise result type for this method, users should annotate it explicitly:

\begin{lstlisting}
type Foo[X] = X match
  case Int => String
  case String => Int

def foo[X](x: X): Foo[X] = x match
  case x: Int => x.toString
  case x: String => x.toInt
\end{lstlisting}

### 2022-04-19 symposium.tex
Do TODOs

Stephanie Weirich presented on several occasions a regular expression library as an example of a dependently-typed program written in Haskell \citep{weirich2014examples}.
The library provides safety guarantees similar to ours, but from the slightly different angle of named-capturing groups.
% TODO: Rework that sentence
An important conceptual difference is that our approach only focuses on type checking (we rely on Java's regular expressions at run-time), whereas her library also contains a complete regular expression engine.

>>>>

Stephanie Weirich presented on several occasions a regular expression library as an example of a dependently-typed program written in Haskell \citep{weirich2014examples}.
The library provides safety guarantees similar to ours, but from the slightly different angle of named-capturing groups.
An important conceptual difference between both approaches is ours only focuses on type checking (we rely on Java's regular expressions at run-time), whereas hers also includes a fully-fledged regular expression engine.
